---
title: "Homework 5"
author: "Ashwini Varghese"
date: "2022-11-16"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1:



## Problem 2:

```{r}
homicides = read.csv("./homicide-data.csv")

```

The raw dataset `homicides` contains `r ncol(homicides)` variables and `r nrow(homicides)` observations. It describes information on homicides from 50 large US cities. Variables of interest include the case ID, the date of the incident, information on the victim (name, race, age and sex), information on the location of the homicide, and the disposition of the case. 

We will create a new variable `city_state`.

```{r}
new_homi <- homicides %>%
  unite("city_state", city:state, sep = ", ", remove = FALSE)
```

We will first look at the total number of homicides in a city and then at the number of homicides that are unsolved in a city.

```{r}
new_homi %>% 
  group_by(city) %>%
  summarize(count = n()) %>%
  knitr::kable(digits = 1)

new_homi %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  group_by(city) %>%
  summarize(count = n()) %>%
  knitr::kable(digits = 1)
```

`prop.test`

```{r}
new_homi %>%
  filter(city_state == "Baltimore, MD") %>%
  summarize(count = n())

new_homi %>%
  filter(city_state == "Baltimore, MD") %>%
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>%
  summarize(count = n())

```

From the above code, we see that in the city of Baltimore, MD, there were a total of 2827 homicides and of those homicides, 1825 were unsolved. We can use `prop.test` to estimate the proportion of homicides that are unsolved and its confidence interval.

```{r}
Balt_test <- prop.test(1825, 2827) %>%
  broom::tidy() %>%
  select(estimate, starts_with("conf"))
```

The proportion of homicides that are unsolved is 0.646 with a confidence interval of 0.628 and 0.663.

```{r}
homi_nest =
  new_homi %>% 
  relocate(city_state) %>% 
  nest(data = uid:disposition)

prop = function(df) {

  data_result = df %>% 
    summarize(total = n(),
              unsolved = sum(disposition %in% c("Closed without arrest", "Open/No arrest")))
    
  prop_results = 
    prop.test(x = data_result %>% pull(unsolved), 
              n = data_result %>% pull(total))

  return(prop_results)
}


final <- homi_nest %>% 
  mutate(results = map(data, prop),
         estimates = map(results, broom::tidy)) %>% 
  select(city_state, estimates) %>% 
  unnest(estimates) %>%
  select(city_state, estimate, starts_with("conf"))


final %>% 
  filter(city_state != "Tulsa, AL") %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
    geom_line() +
    geom_point()+
    geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width=.2,
                 position=position_dodge(0.05))+
    theme(axis.text.x = element_text(angle = 90))

```


```{r}
#rnorm(n = 30, mean = 0, sd = 5)

#rerun(5000, rnorm(n = 30, mean = 0, sd = 5))

trial = function(mu) {
  
  tibble_df = 
    tibble(x = rnorm(n = 30, mean = mu, sd = 5))
  t.test(tibble_df) %>% 
    broom::tidy() %>% 
    select(estimate, p.value)
}

expand.grid(mu = 0, run = 1:5000) %>% 
  mutate(value = map(mu, trial)) %>%
  unnest(value)



```










